---
title: "simulations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('./R/sim.func.rate.R')
source('./R/mod.func.R')
source('./R/jags_mod1.R')
source('./R/jags_mod1a.R')

source('./R/jags_mod2.R')
source('./R/jags_mod3.R')

source('./R/call_jags.R')
source('./R/process_jags.R')

library(dplyr)
library(reshape2)
library(rjags)
library(HDInterval)
library(pbapply)
```

Generate cases and control with different VEs
```{r}
test.vax.irr <- c(0.2, 0.4, 0.6, 0.8, 1.0)

all.pops <- lapply(test.vax.irr,sim.func.rate) 

combine_pop <- dplyr::bind_rows(all.pops)
```

Run model on each dataset individually
```{r}

t(sapply(all.pops, mod.func))
```

OR same model on combined dataset
```{r}
mod.res1 <- mod.func(combine_pop)
mod.res1
```



In more complicated case, we could have a very large number of categories,  each with a different vax.irr, which depends on distance
```{r}
test.irr <- seq(from=0.05, to=0.95, by=0.01)

many.pops <- pblapply(test.irr,sim.func.rate)

many.pops.combined <- dplyr::bind_rows(many.pops)

```


```{r}
mod.res.many <- t(pbsapply(many.pops,mod.func ))
```

```{r}
plot(mod.res.many[,1], mod.res.many[,2], xlab='IRR', ylab='dist')
abline(a=0, b=1)
```
## Multinomial JAGS model

Categorize case by distance.
```{r}
str(many.pops.combined)

many.pops.combined$dist_category <- NA

many.pops.combined$dist_category[many.pops.combined$dist>=0 & many.pops.combined$dist <= 0.1] <- 1

many.pops.combined$dist_category[many.pops.combined$dist>0.1 & many.pops.combined$dist <= 0.2] <- 2

many.pops.combined$dist_category[many.pops.combined$dist>0.2 & many.pops.combined$dist <= 0.3] <- 3

many.pops.combined$dist_category[many.pops.combined$dist>0.3 & many.pops.combined$dist <= 0.4] <- 4

many.pops.combined$dist_category[many.pops.combined$dist>0.4 & many.pops.combined$dist <= 0.5] <- 5

many.pops.combined$dist_category[many.pops.combined$dist>0.5 & many.pops.combined$dist <= 0.6] <- 6

many.pops.combined$dist_category[many.pops.combined$dist>0.6 & many.pops.combined$dist <= 0.7] <- 7

many.pops.combined$dist_category[many.pops.combined$dist>0.7 & many.pops.combined$dist <= 0.8] <- 8

many.pops.combined$dist_category[many.pops.combined$dist>0.8 & many.pops.combined$dist <= 0.9] <- 9

many.pops.combined$dist_category[many.pops.combined$dist>0.9 & many.pops.combined$dist <= 1.0] <- 10

many.pops.combined$dist_category[many.pops.combined$case==0] <- 11  #CONTROLS

cat.pop1 <- many.pops.combined %>%
  group_by(vax,dist_category) %>%
  summarize(N_people = n(), ave_dist=mean(dist))

cat.pop1.m <- 
  reshape2::melt(cat.pop1, id.vars=c('vax','dist_category'))

cat.pop1.c <- 
  reshape2::acast(cat.pop1.m, dist_category ~ vax ~variable)

```
Estimate each group independently 

```{r, eval=F}
mod1 <- call_jags(set.mod=jags_mod1)

jags_mod1_post <- process_jags(mod1)
jags_mod1_post
```

Impose an AR(1) structure on the effect of vaccination by distance
```{r, eval=F}
mod2 <- call_jags(set.mod=jags_mod1a)

jags_mod2_post <- process_jags(mod2)
jags_mod2_post
```

AR(1) random slope and explicitly incorporate genetic distance. eac category gives effect VS REFERENCE not vs the next category

```{r}
# mod3 <- call_jags(set.mod=jags_mod3, distvar=cat.pop1.c[,1,2], keep.parms=c('overall_vax_effect','sero_vax_effect','rho','beta1','delta0','delta1'))
# 
# jags_mod3_post <- process_jags(mod3)
# jags_mod3_post
```



