---
title: "simulations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('./R/sim.func.rate.R')
source('./R/mod.func.R')

```

Generate cases and control with different VEs
```{r}
test.vax.irr <- c(0.2, 0.4, 0.6, 0.8, 1.0)

all.pops <- lapply(test.vax.irr,sim.func.rate) 

combine_pop <- dplyr::bind_rows(all.pops)
```

Run model on each dataset individually
```{r}

t(sapply(all.pops, mod.func))
```

OR same model on combined dataset
```{r}
mod.res1 <- mod.func(combine_pop)
mod.res1
```



In more complicated case, we could have a very large number of categories,  each with a different vax.irr, which depends on distance
```{r}
test.irr <- seq(from=0.05, to=0.95, by=0.01)

many.pops <- lapply(test.irr,sim.func.rate)
```

```{r}
mod.res.many <- t(sapply(many.pops,mod.func ))
```

```{r}
plot(mod.res.many[,1], mod.res.many[,2])
```

```{r}
many.pops.combined <- dplyr::bind_rows(many.pops)
mod.res2 <- mod.func(many.pops.combined)
mod.res2
```
try a model with interaction of ditsance and vax effect--does not work well.
```{r}

#for controls, assume distance= ave distance of cases
many.pops.combined$dist.impute <- many.pops.combined$dist
#assgn ave distance among unvaccinated cases to the controls


many.pops.combined$dist.impute[many.pops.combined$y==0] <- mean(many.pops.combined$dist[many.pops.combined$y==1 & many.pops.combined$vax==0])

mod2 <- glm(case ~ vax*dist.impute, family='binomial', data=many.pops.combined)

summary(mod2)

exp(mod2$coefficients['vax'] + mod2$coefficients['vax:dist.impute']*0.05)

exp(mod2$coefficients['vax'] + mod2$coefficients['vax:dist.impute']*0.95)
```


#vax as a predictor of case status and as a predictor of distance among the vaccinated, similar to ginny's approach

```{r}
mod2 <- glm(case ~ vax, family='binomial', data=many.pops.combined)

mod3 <- mgcv::gam(vax ~ s(dist), family='binomial', data=many.pops.combined[many.pops.combined$case==1,])

summary(mod3)

plot(mod3, ylab='proportion vaccinated', xlab='Distance from vaccine strain', bty='l')

pred.vax <- predict(mod3, type='response')
```

```{r}
#for controls:
#Set to observed values
many.pops.combined$pred.vax[many.pops.combined$case==0] <- many.pops.combined$vax[many.pops.combined$case==0] # for controls use observed vaccine status
#many.pops.combined$pred.vax[many.pops.combined$y==0] <- many.pops.combined$vax[many.pops.combined$y==0] # for controls use observed vaccine status

ave.effect.vax <- exp(coef(mod2)['vax']) #average effect of vaccination comparing cases and test negative controls; 
#represent all circulating strains regardless of distance/avrage distance
range.prop.vax <- range(pred.vax) #estimated proportion vaccinated by distance
#when dist=0
mean.prop.vax=mean(pred.vax)
range.prop.vax.ctr <- range.prop.vax- mean.prop.vax
exp(coef(mod2)['vax'] + range.prop.vax.ctr) 

```

## Zero-inflated beta regression (Ginny's approach)
```{r}
#install.packages('zoib')
library(zoib)

eg1.fixed <- zoib(case ~ 1+ vax | 1 |1+vax, data = many.pops.combined, joint = FALSE,
random = 0,  zero.inflation = TRUE,
one.inflation = FALSE, n.iter = 1050, n.thin = 5, n.burn = 50)

sample1 <- eg.fixed$coeff
# check convergence of the MCMC chains
traceplot(sample1); autocorr.plot(sample2); gelman.diag(sample1)
```



